%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
\documentclass[11pt, a4paper]{awesome-cv}
\usepackage[hidelinks]{hyperref}

\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}
% ---- Marca / color (elige uno) ----
\definecolor{xboxgreen}{HTML}{107C10} % Xbox green
\colorlet{awesome}{xboxgreen}         % o awesome-red / awesome-skyblue
\setbool{acvSectionColorHighlight}{true}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

% ---- Contraste más oscuro ----
\definecolor{darktext}{HTML}{1A1A1A}
\colorlet{text}{darktext}
\colorlet{graytext}{darktext}
\colorlet{lighttext}{darktext}
\renewcommand*{\lettertextstyle}{\fontsize{10pt}{1.45em}\bodyfontlight\upshape\color{darktext}}
\renewcommand*{\lettersectionstyle}[1]{{\fontsize{14pt}{1em}\bodyfont\bfseries\color{darktext}#1}}

% --- Header ---
\name{Juan Manuel}{Young Hoyos}
\position{Frontend Software Engineer {\enskip\cdotp\enskip} React | TypeScript | Gaming UX}
\address{Medellín, Colombia \,·\, Open to Costa Rica / Remote LATAM}
\mobile{+57 314 415 4399}
\email{juanmanuel12.13jmyh81@gmail.com}
\homepage{jmyounghoyos.com}
\github{Youngermaster}
\linkedin{juan-manuel-young-hoyos}

% --- Letter meta ---
\recipient{Microsoft — Team Xbox}{Front End Software Engineer (Job \#1855291)}
\letterdate{\today}
\lettertitle{Application for Front End Software Engineer — Xbox}
\letteropening{Dear Xbox Hiring Team,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Resume: Juan-Manuel-Young-Hoyos\_Xbox-Frontend\_MS-1855291.pdf}

\begin{document}
\makecvheader[R]
\makelettertitle

\begin{cvletter}

I decided to become a software engineer the same way I learned to love games: \textbf{solving puzzles and building things}. As a kid I spent hours in \textbf{LEGO Star Wars}, tinkering with how levels fit together and wondering how the game worked under the hood. Years later, when I saw this opening at \textbf{Microsoft Xbox}, I applied immediately. I admire Microsoft as a technology leader and Xbox even more because I grew up hosting \textbf{Halo 3} LAN parties in my town, playing with a split screen \textbf{Call of Duty: Modern Warfare 3} with my friends and beating \textbf{Gears of War 2/3} on Insane with my brother. That feeling of shared magic is what I want to help players feel through great \textbf{UI/UX} here when in a few months I join the Xbox team.

On the engineering side, I build \textbf{cross-platform} experiences with \textbf{React.js, React Native, and TypeScript}, designed for \textbf{responsive UX across device form factors} and \textbf{multi-input support} (gamepad, touch, mouse/keyboard). At \textbf{Publicis Global Delivery}, I shipped React Native features for the \textbf{Wegmans} app that lifted engagement by \textbf{30\%}, reduced critical bugs by \textbf{25\%} with \textbf{Jest}+\textbf{Dynatrace}, and cut release cycles by \textbf{50\%} via \textbf{GitHub Actions} CI/CD. I also led a \textbf{Next.js + TypeScript} redesign (Duluth Trading Company), improved performance in \textbf{Nuxt.js} apps, and built \textbf{GameConnect} UI/UX patterns with multi-input. I’m comfortable integrating \textbf{cloud service dependencies} on \textbf{Azure}, and I have practical exposure to \textbf{C\# / C++} from academic and side projects.

I’m fluent in English and Spanish, care deeply about accessibility and inclusive design, and I’m available to work on-site in Colombia or for \textbf{remote LATAM} and \textbf{open to Costa Rica}. I’d be proud to contribute to Xbox Experiences \& Platforms and help the next generation feel the same magic I felt growing up.

\end{cvletter}

\makeletterclosing
\end{document}
