%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
\newcommand{\quotes}[1]{``#1''}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
{Machine Learning Engineer} % Job title
{Game Connect} % Organization
{Medellín} % Location
{Aug. 2023 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Spearheaded sentiment analysis initiatives, processing user comments to gain insights into user preferences, feedback, and overall gaming experience.}
    \item {Designed and implemented recommendation algorithms that provide game suggestions based on diverse gaming topics and user behavior, enhancing user engagement.}
    \item {Currently developing API endpoints to integrate machine learning models, facilitating third-party access and application, even though it's not yet in a production-ready state.}
    \item {Collaborated closely with a cross-functional team, ensuring the efficient integration of ML models into the platform's ecosystem and optimizing model performance based on live feedback.}
  \end{cvitems}
}
%---------------------------------------------------------
%---------------------------------------------------------
\cventry
{FullStack Developer} % Job title
{Design Systems Inno} % Organization
{Medellín} % Location
{Jan. 2023 - Sep. 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Led full-stack development across diverse projects, harnessing FastAPI, TypeScript, Node for backend and React for frontend applications.}
    \item {Integrated machine learning models with application backends to provide data-driven insights to end users.}
    \item {Optimized data processing and storage mechanisms to facilitate efficient data retrieval for AI modeling and analysis.}
  \end{cvitems}
}
%---------------------------------------------------------

%---------------------------------------------------------
\cventry
{IoT Technician} % Job title
{Fire Block Labs} % Organization
{Medellín} % Location
{Oct. 2021 - May 2022} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Developed IoT devices and networks tailored for diverse crops, capturing essential environmental variables.}
    \item {Enabled AI-driven analysis by transmitting the captured data to a cloud server, facilitating real-time crop monitoring and traceability.}
    \item {Collaborated with a data analytics team to use the captured data for predictive modeling and optimization strategies.}
  \end{cvitems}
}
%---------------------------------------------------------

%---------------------------------------------------------
\cventry
{Electronics Technician} % Job title
{Coraltech S.A.S} % Organization
{Medellín} % Location
{May 2020 - Sept. 2020} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Engineered a cost-efficient wearable microcontroller to determine geolocation coordinates with a precision that did not exceed one meter of error.}
    \item {Utilized advanced data algorithms to ensure the accuracy and reliability of geolocation data for applications needing high precision.}
    \item {Collaborated with the data science team to analyze geolocation data for potential applications in AI and predictive analysis.}
  \end{cvitems}
}
%---------------------------------------------------------

\end{cventries}
