\cvsection{Experience}
\newcommand{\quotes}[1]{``#1''}

\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Frontend Developer}
  {Publicis Global Delivery (PGD) — assigned to Digitas}
  {Colombia (Remote)}
  {Jan. 2025 -- Present}
  {
    \begin{cvitems}
      \item {Led the redesign of Duluth Trading Company's e-commerce using \textbf{Next.js} + \textbf{TypeScript}, improving load performance and delivering \textbf{responsive UX} across desktop / tablet / mobile.}
      \item {Shipped production features and stability fixes to an internal \textbf{AI agent web app} (\textbf{Nuxt.js}), improving workflow reliability for distributed teams.}
      \item {Owned the full delivery loop: implementation, code review, performance tuning, and rollout with CI/CD.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {React Native Developer}
  {Publicis Global Delivery (PGD) — assigned to Razorfish / Wegmans}
  {Colombia (Remote \textemdash{} New York, USA)}
  {Dec. 2023 -- Dec. 2024}
  {
    \begin{cvitems}
      \item {Delivered \textbf{production React Native features} at scale for Wegmans Food Markets, Inc.; modular components (\textbf{TypeScript}, \textbf{Zustand}, \textbf{Algolia}) increased in-app engagement by \textbf{30\%}.}
      \item {Improved app reliability by integrating \textbf{Dynatrace} observability and \textbf{Jest} unit tests, cutting critical bugs by \textbf{25\%} and reducing regression risk.}
      \item {Automated \textbf{CI/CD} with GitHub Actions for Android/iOS builds and releases, reducing release cycle time by \textbf{50\%} and supporting iterative delivery.}
      \item {Implemented responsive, accessible UI for touch and keyboard input, focusing on performance and predictable state.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Full Stack Developer (Self-employed)}
  {Grisú}
  {Colombia (Remote)}
  {Jul. 2023 -- Present}
  {
    \begin{cvitems}
      % \item {Designed and built features for \textbf{GameConnect}, a gaming-style social/discovery experience using \textbf{React} + \textbf{TypeScript}.}
      \item {Developed full-stack web apps with \textbf{NestJS} + \textbf{React}; shipped to \textbf{Azure} with \textbf{cloud service dependencies} and secured CI/CD pipelines.}
      \item {Worked directly with stakeholders (including public-sector programs in Curaçao) to gather requirements, build quickly, and iterate.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Full Stack Developer (Part-time)}
  {ArcDesign}
  {Spain (Remote)}
  {Jul. 2023 -- Mar. 2025}
  {
    \begin{cvitems}
      \item {Implemented a geolocation / dispatch algorithm (hashmaps + geohashes) that improved lookup scalability and positional accuracy by \textbf{70\%}.}
      \item {Integrated that logic into a \textbf{React Native} mobile client to deliver \textbf{low-latency, near real-time} UX with a game-like feel.}
      \item {Deployed production React applications on AWS/Hostinger with attention to uptime, cost, and maintainability.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Problem Solver / Full Stack Developer}
  {Design Systems Inno}
  {Colombia}
  {Dec. 2022 -- Jun. 2023}
  {
    \begin{cvitems}
      \item {Built \textbf{cloud-ready services} with \textbf{RabbitMQ} + \textbf{MongoDB} for real-time message processing.}
      \item {Reduced React / Angular bundle sizes by \textbf{70\%}, improving page load time and helping the team scale features faster.}
      \item {Improved Dockerization and CI/CD pipelines to increase deployment consistency.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Cyber Security Analyst}
  {Geta Club Play}
  {Colombia (Remote)}
  {Sep. 2021 -- Jun. 2022}
  {
    \begin{cvitems}
      \item {Introduced \textbf{DevSecOps} practices (\textbf{OWASP ZAP}, \textbf{SonarQube}) that cut security vulnerabilities by \textbf{50\%} in four months.}
      \item {Reverse-engineered Android APKs to detect data exposure paths and prevent leaks, reducing critical findings by \textbf{40\%}.}
      \item {Helped draft ISO/27001-aligned security processes for mobile products.}
    \end{cvitems}
  }

\end{cventries}
