%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Red Teamer} % Job title
    {Aligo Defensores Informáticos} % Organization
    {In person, Colombia} % Location
    {Aug. 2022 - Oct. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Pentesting websites.}
        \item {Pentesting tooling development (Rust and Nim).}
        \item {Phishing campaigns developed.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cyber Security Analyst} % Job title
    {GETA Club Play} % Organization
    {Remote, Colombia} % Location
    {Oct. 2021 - Jun. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I used the DAST capabilities of OWASP ZAP to automatically review the company's web
        applications.}
        \item {I used SonarQube's SAST capabilities to automatically review the company's code.}
        \item {I developed an "economic" DevSecOps pipeline to avoid possible common 
        vulnerabilities.}
        \item {I worked closely with the AI team to sanitize requests made by users and avoid SQL
        injections.}
        \item {With some limited resources I Worked closely with IT to implement a good password 
        policy (KeePass).}
        \item {I Worked closely with IT to implement backup policies for employee files and
        repositories.}
        \item {I was given an external pentesting report with about 800 vulnerabilities in our
        projects, and I reduced that number to less than 390 (i.e. fixed about 50\% of
        vulnerabilities) in a span of 4 months.}
        \item {I simulated and implemented reverse engineering attacks on some project APKs in order
        to address, together with the development team, a possible way to mitigate the possibility
        of a Hacker obtaining useful or critical information about our core business.}
        \item {Together with the IT team, I developed a Security Plan based on the ISO/27001
        standard.}
        \item {I managed the Office 365 Admin console to control the licenses and Microsoft 
        accounts.}
        \item {I implemented hardening for some of our infrastructure processes.}
        \item {I worked alongside the IA team to develop a part of the SOC (Security Operations
        Center) that can deliver value to our technical and non-technical employees.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cyber Security Trainee} % Job title
    {GETA Club Play} % Organization
    {Remote, Colombia} % Location
    {Aug. 2021 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I did a Cyber security planning for 4 months to 3 company's products.}
        \item {I found and reported common OWASP based vulnerabilities.}
        \item {I worked along with the development team to fix the vulnerabilities found.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Quality Assurance Tester} % Job title
    {GETA Club Play} % Organization
    {Remote, Colombia} % Location
    {Feb. 2021 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I captured 100+ bugs within the span of 4 months while conducting quality assurance
        testing on 7 company products thereby increasing the acceptance criteria of the top-rung
        corporate “chiefs”.}
        \item {I document and record analyzed bugs for quality assurance every week.}
        \item {I worked closely on 3 projects with development team to write test plans for quality
        assurance.}
        \item {I performed more than 15\% testing through automation and remaining testing manually
        using Selenium.}
        \item {I led a 4-member team in providing quality assurance on 3 projects closely with
        development team.}
        \item {I refactored and retrofitted legacy a C++ WebAssembly application, improving code
        quality by 45\%.}
        \item {I completed more than 20 "Desk Checks" to reduce on 25\% the amount of Pull Request
        and therefore save the Tech Lead's time.}
        \item {I helped to document 2 Unity 3D projects and also checked a documentation of an 
        Angular/.Net Core project.}
        \item {I did functional, online, manual, usability and stress tests.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
