%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
\newcommand{\quotes}[1]{``#1''}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Full Stack Developer} % Job title
  {Grisú} % Organization
  {Self-employed, Colombia} % Location
  {Jul. 2023 - Present (Aug. 2023)} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed and developed a React Native App to simulate the Yak Bak 90's toy.}
      \item {Designed and developed Tap it! a React Native simple game to test out your reflexes.}
      \item {Engineered the company's Landing Page using React, ensuring a modern, user-centric design.}
      \item {Designed, developed, and deployed a React Sudoku Solver web app, providing users with intuitive puzzle-solving assistance.}
      \item {Rolled out a dynamic React Letter Soup solver and generator, utilizing React for seamless web functionality.}
      \item {Actively driving the development of an engaging Hyper-Casual game using Unity 3D.}
      \item {Implementing a generic backend for several future apps and services using self-hosted Supabase.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Full Stack Developer} % Job title
  {ArcDesign} % Organization
  {Part-time, Spain} % Location
  {Jul. 2023 - Present (Aug. 2023)} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Innovated an \quotes{advanced algorithm} using hashmaps and geohashes, significantly enhancing the application's performance and scalability.}
      \item {Spearheaded architectural design, incorporating MQTT and conducting simulations in Python.}
      \item {Integrated the \quotes{advanced algorithm} within a React Native environment for superior mobile performance (https://hiwayapp.io).}
      \item {Led the development and deployment of static webs on AWS and Hostinger, employing React (https://arcdesign.io).}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Problem Solver} % Job title
  {Design Systems Inno} % Organization
  {Contract, Colombia} % Location
  {Jan. 2023 - Jun. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Architected a system for internal APIs, using RabbitMQ for asynchronous task management. Clients receive ID tickets for tracking while the backend efficiently handles web scraping and parsing, ensuring timely user feedback.}
      \item {Developed internal APIs to automate some internal processes using Go Fiber, Python Fast API, and MongoDB.}
      \item {Created web scraping tools and custom HTML parsers in Python using Playwright and Beautiful Soup.}
      \item {Paired with partners to fix critical bugs, ensuring on-time software deliveries and maintaining high quality.}
      \item {Developed an automation script in Python for efficient contract signing.}
      \item {Developed various administration panels using React (Redux + Saga).}
      \item {Optimized project builds for some React web applications, reducing build sizes from 3.46 MB to around 886 KB and in some others even a little bit more.}
      \item {I Assisted in improving the quality and speed of Dockerfiles for React and Angular web applications.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Security Consultant} % Job title
  {Design Systems Inno} % Organization
  {Contract, Colombia} % Location
  {Dec. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed an external penetration testing engagement for a week and a half.}
      \item {Documented the findings in the software and part of the infrastructure.}
      \item {Documented some advices to improve the software and infrastructure quality}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Red Teamer} % Job title
  {Aligo Defensores Informáticos} % Organization
  {In person, Colombia} % Location
  {Aug. 2022 - Oct. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Pentesting websites.}
      \item {Pentesting tooling development (Go and Nim).}
      \item {Phishing campaigns developed.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Cyber Security Analyst} % Job title
  {GETA Club Play} % Organization
  {Remote, Colombia} % Location
  {Oct. 2021 - Jun. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {I used the DAST capabilities of OWASP ZAP to automatically review the company's web
                  applications.}
      \item {I used SonarQube's SAST capabilities to automatically review the company's code.}
      \item {I developed an "economic" DevSecOps pipeline to avoid possible common
                  vulnerabilities.}
      \item {I worked closely with the AI team to sanitize requests made by users and avoid SQL
                  injections.}
      \item {With some limited resources I Worked closely with IT to implement a good password
                  policy (KeePass).}
      \item {I Worked closely with IT to implement backup policies for employee files and
                  repositories.}
      \item {I was given an external pentesting report with about 800 vulnerabilities in our
                  projects, and I reduced that number to less than 390 (i.e. fixed about 50\% of
                  vulnerabilities) in a span of 4 months.}
      \item {I simulated and implemented reverse engineering attacks on some project APKs in order
                  to address, together with the development team, a possible way to mitigate the possibility
                  of a Hacker obtaining useful or critical information about our core business.}
      \item {Together with the IT team, I developed a Security Plan based on the ISO/27001
                  standard.}
      \item {I implemented hardening for some of our infrastructure processes.}
      \item {I worked alongside the IA team to develop a part of the SOC (Security Operations
                  Center) that can deliver value to our technical and non-technical employees.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Cyber Security Trainee} % Job title
  {GETA Club Play} % Organization
  {Remote, Colombia} % Location
  {Aug. 2021 - Sep. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {I did a Cyber security planning for 4 months to 3 company's products.}
      \item {I found and reported common OWASP based vulnerabilities.}
      \item {I worked along with the development team to fix the vulnerabilities found.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Software Quality Assurance Tester} % Job title
  {GETA Club Play} % Organization
  {Remote, Colombia} % Location
  {Feb. 2021 - Aug. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {I captured 100+ bugs within the span of 4 months while conducting quality assurance
                  testing on 7 company products thereby increasing the acceptance criteria of the top-rung
                  corporate “chiefs”.}
      \item {I document and record analyzed bugs for quality assurance every week.}
      \item {I performed more than 15\% testing through automation and remaining testing manually
                  using Selenium.}
      \item {I refactored and retrofitted legacy a C++ WebAssembly application, improving code
                  quality by 45\%.}
      \item {I completed more than 20 "Desk Checks" to reduce on 25\% the amount of Pull Request
                  and therefore save the Tech Lead's time.}
      \item {I helped to document 2 Unity 3D projects and also checked a documentation of an
                  Angular/.Net Core project.}
      \item {I did functional, online, manual, usability and stress tests.}
    \end{cvitems}
  }
  %---------------------------------------------------------
\end{cventries}
