%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
\documentclass[11pt,a4paper]{awesome-cv}
\usepackage[hidelinks]{hyperref}

\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}
\colorlet{awesome}{awesome-red}
\setbool{acvSectionColorHighlight}{true}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\definecolor{darktext}{HTML}{1A1A1A}
\colorlet{text}{darktext}
\renewcommand*{\lettertextstyle}{\fontsize{10pt}{1.45em}\bodyfontlight\upshape\color{darktext}}
\renewcommand*{\lettersectionstyle}[1]{{\fontsize{14pt}{1em}\bodyfont\bfseries\color{darktext}#1}}

% --- Header info ---
\name{Juan Manuel}{Young Hoyos}
\position{Senior Web UI Developer — React / TypeScript / Cloud}
\address{Medellín, Colombia · Open to Remote or Hybrid}
\mobile{+57 1234567890}
\email{juanmanuel12.13jmyh81@gmail.com}
\homepage{jmyounghoyos.com}
\github{Youngermaster}
\linkedin{juan-manuel-young-hoyos}

% --- Letter meta ---
\recipient
  {Hiring Team}
  {Globant}
\letterdate{\today}
\lettertitle{Application for Senior Web UI Developer}
\letteropening{Dear Globant Hiring Team,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Resume — Juan Manuel Young Hoyos.pdf}

\begin{document}
\makecvheader[R]
\makelettertitle

\begin{cvletter}

I am excited to apply for the \textbf{Senior Web UI Developer} position at Globant. With over \textbf{4 years of experience building scalable, high-quality interfaces} using \textbf{React}, \textbf{TypeScript}, and modern web technologies, I’m passionate about creating seamless user experiences that align technology with business impact.

At \textbf{Publicis Global Delivery}, I have delivered production-grade React Native and Next.js applications for international clients like \textbf{Wegmans Food Markets} and \textbf{Duluth Trading Company}. My work includes implementing predictable state management (Zustand), writing Jest tests, integrating CI/CD pipelines with GitHub Actions, and improving accessibility and performance across devices.  

Before that, at \textbf{Design Systems Inno}, I worked across both \textbf{React and Angular} environments, optimizing builds, modularizing UI components, and enabling scalable delivery through Docker-based workflows. These experiences have made me fluent in the fundamentals of modern web engineering — HTML5, CSS3, TypeScript — and adaptable across frameworks, including Vue and Angular.

I’m especially drawn to Globant’s vision of transforming industries through innovation and design-led technology. I would love to contribute to projects where technical excellence meets creativity and help shape digital experiences that make a difference.

Thank you for your time and consideration. I would be delighted to bring my technical depth, UI craftsmanship, and collaborative mindset to Globant’s engineering teams.

\end{cvletter}

\makeletterclosing
\end{document}
