%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
\documentclass[11pt, a4paper]{awesome-cv}
\usepackage[hidelinks]{hyperref}

\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}
% ---- Marca / color (elige uno) ----
\definecolor{xboxgreen}{HTML}{107C10} % Xbox green
\colorlet{awesome}{xboxgreen}         % o awesome-red / awesome-skyblue
\setbool{acvSectionColorHighlight}{true}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

% ---- Contraste más oscuro ----
\definecolor{darktext}{HTML}{1A1A1A}
\colorlet{text}{darktext}
\colorlet{graytext}{darktext}
\colorlet{lighttext}{darktext}
\renewcommand*{\lettertextstyle}{\fontsize{10pt}{1.45em}\bodyfontlight\upshape\color{darktext}}
\renewcommand*{\lettersectionstyle}[1]{{\fontsize{14pt}{1em}\bodyfont\bfseries\color{darktext}#1}}

% --- Header ---
\name{Juan Manuel}{Young Hoyos}
\position{Software Engineer II - Fronted {\enskip\cdotp\enskip} React | TypeScript | Gaming UX}
\address{Medellín, Colombia \,·\, Open to Costa Rica / Remote LATAM}
\mobile{+57 1234567890}
\email{juanmanuel12.13jmyh81@gmail.com}
\homepage{jmyounghoyos.com}
\github{Youngermaster}
\linkedin{juan-manuel-young-hoyos}

% --- Letter meta ---
\recipient{Microsoft — Team Xbox}{Front End Software Engineer (Job \#1891629)}
\letterdate{\today}
\lettertitle{Application for Front End Software Engineer — Xbox}
\letteropening{Dear Xbox Hiring Team,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Resume: Juan-Manuel-Young-Hoyos\_Xbox-Frontend\_MS-1891629.pdf}

\begin{document}
\makecvheader[R]
\makelettertitle

\begin{cvletter}

I am applying for the Software Engineer II position (Job \#1891629) at Xbox because I combine the technical skills you require with genuine passion for gaming experiences. I have \textbf{3+ years shipping cross-platform React applications} with \textbf{TypeScript}, expertise in \textbf{responsive UX across device form factors}, and hands-on experience with \textbf{multi-input navigation} (gamepad, touch, mouse/keyboard). Growing up hosting \textbf{Halo 3} LAN parties, playing split-screen \textbf{Call of Duty: Modern Warfare 3}, and beating \textbf{Gears of War 2/3} on Insane with my brother shaped my understanding of what makes gaming experiences compelling—and now I want to help build them at Xbox.

On the engineering side, I build \textbf{cross-platform} experiences with \textbf{React.js, React Native, and TypeScript}, designed for \textbf{responsive UX across device form factors} and \textbf{multi-input support} (gamepad, touch, mouse/keyboard). At \textbf{Publicis Global Delivery}, I shipped React Native features for \textbf{Wegmans} that lifted engagement by \textbf{30\%}, reduced critical bugs by \textbf{25\%} with \textbf{Jest}+\textbf{Dynatrace}, and cut release cycles by \textbf{50\%} via \textbf{GitHub Actions CI/CD}. I implemented \textbf{asynchronous programming patterns} and \textbf{state management} (\textbf{Zustand}) to deliver smooth, responsive experiences. I also led a \textbf{Next.js + TypeScript} redesign (Duluth Trading Company), and at \textbf{Grisú} I deployed \textbf{React apps on Azure} with \textbf{cloud service dependencies} and secure deployment pipelines. Through \textbf{GameConnect}, I built gaming UI/UX with multi-input navigation patterns. I have practical exposure to \textbf{C\# / C++} from academic and side projects.

I'm fluent in English and Spanish, care deeply about accessibility and inclusive design, and I'm available to work on-site in Colombia or for \textbf{remote LATAM} and \textbf{open to Costa Rica}. I'd be proud to contribute to Xbox Experiences \& Platforms and help deliver the compelling experiences that define Xbox for the next generation of gamers.

\end{cvletter}

\makeletterclosing
\end{document}
