%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
\newcommand{\quotes}[1]{``#1''}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Full-Stack Developer} % Job title
{Freelance} % Organization
{Medellín, Colombia} % Location
{Feb. 2024 - Apr. 2025} % Date(s)
{
  \begin{cvitems}
    \item {Developed a full-stack auction platform using \textbf{NestJS (GraphQL)} and \textbf{React}, enabling real-time bidding and seamless user interaction.}
    \item {Implemented state management and side-effect handling using \textbf{Redux Sagas} for optimal UX.}
    \item {Built a subsidy application platform using \textbf{Next.js} and \textbf{Node.js (Express)}, with secure, validated multi-step forms.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Full-Stack Developer} % Job title
{Mappa Medellín} % Organization
{Medellín, Colombia} % Location
{Jan. 2025 - Mar. 2025} % Date(s)
{
  \begin{cvitems}
    \item {Improved AI chat job candidate platform using \textbf{tRPC}, \textbf{Next.js}, and \textbf{Jotai} for state management.}
    \item {Enhanced backend performance in \textbf{Node.js}, updated PostgreSQL schema and optimized data handling.}
    \item {Built modules for candidate management software using the same stack.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Full-Stack and Mobile Developer} % Job title
{Sancrisoft} % Organization
{Medellín, Colombia} % Location
{Oct. 2023 - Feb. 2024} % Date(s)
{
  \begin{cvitems}
    \item {Rebuilt a volunteer mobile app using \textbf{React Native CLI} (v0.59 to 0.71) with \textbf{Redux Sagas} for efficient state control.}
    \item {Enhanced a flight simulation platform UI with \textbf{React} and \textbf{Redux Toolkit}.}
    \item {Improved backend services using \textbf{Node.js}, \textbf{Fastify}, and SQL for faster responses and robust data ops.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Co-Founder and Full-Stack Developer (Mobile Focus)} % Job title
{Design Systems Inno} % Organization
{Medellín, Colombia} % Location
{Dec. 2021 - Sep. 2023} % Date(s)
{
  \begin{cvitems}
    \item {Led mobile app development in the insurance and transportation sectors with \textbf{React Native CLI + TypeScript + Context API}.}
    \item {Directed a React + Redux Sagas inventory dashboard with \textbf{FastAPI + MongoDB} backend.}
    \item {Built a live-tracking school transport app using \textbf{MQTT}, \textbf{React Native}, \textbf{Node.js}, and \textbf{MongoDB}.}
    \item {Developed a facial recognition system with \textbf{React Native + AWS Rekognition + MySQL}.}
    \item {Created web apps for real estate and development companies using \textbf{React + Next.js}.}
    \item {Led UI/UX and branding with \textbf{Figma}.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Full-Stack and Mobile Developer} % Job title
{Brain Labs S.A.S} % Organization
{Medellín, Colombia} % Location
{Jan. 2021 - Nov. 2021} % Date(s)
{
  \begin{cvitems}
    \item {Developed web/mobile apps for agricultural IoT with \textbf{React}, \textbf{React Native CLI}, and \textbf{Redux}.}
    \item {Collaborated on backend with \textbf{Node.js} and \textbf{Express} for real-time data processing and device communication.}
  \end{cvitems}
}

\end{cventries}
