%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
\newcommand{\quotes}[1]{``#1''}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Frontend Developer} % Job title
  {Publicis Global Delivery (PGD) assigned to Digitas} % Organization
  {Colombia (Remote)} % Location
  {Jan. 2025 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Building the complete redesign of Duluth Trading Company's e-commerce platform using \textbf{Next.js} and \textbf{TypeScript}, delivering responsive experiences across desktop, tablet, and mobile devices.}
      \item {Implemented Publicis Collective's website redesign using \textbf{Nuxt.js} and \textbf{Contentful}, focusing on performance optimization.}
      \item {Enhanced the \textbf{Nuxt.js} AI agent web app with bug fixes and new features, improving workflow efficiency for marketing teams.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {React Native Developer} % Job title
  {Publicis Global Delivery (PGD) assigned to Razorfish} % Organization
  {Colombia (Remote - New York, USA)} % Location
  {Dec. 2023 - Dec. 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Delivered cross-platform mobile experiences for the \textbf{Wegmans} e-commerce app using \textbf{React Native} and \textbf{TypeScript}, implementing scalable components with \textbf{Zustand} state management and \textbf{Algolia} search integration, achieving a 30\% increase in user engagement.}
      \item {Optimized application performance across devices (phone, tablet) with responsive design, supporting touch and keyboard navigation.}
      \item {Implemented performance monitoring with \textbf{Dynatrace} and unit testing using \textbf{Jest}, improving system reliability and reducing bugs by 25\%.}
      \item {Architected and deployed automated CI/CD pipelines with \textbf{GitHub Actions}, reducing deployment cycles by 50\% across Android and iOS.}
    \end{cvitems}
  }

  %---------------------------------------------------------
 \cventry
  {Full Stack Developer (Self-employed)} % Job title
  {Grisú} % Organization
  {Colombia (Remote)} % Location
  {Jul. 2023 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Built gaming platform solutions for \textit{GameConnect}, creating responsive UI/UX for multiple input methods across different screen sizes.}
      \item {Built cross-platform applications using \textbf{React Native} and \textbf{TypeScript}.}
      \item {Enhanced government web applications for \textit{Curaçao SOAW} using \textbf{Nest.js (TypeScript)} and \textbf{React}, deployed on \textbf{Azure}.}
      % \item {Delivered full-stack solutions with \textbf{React Native}, \textbf{Kafka}, and \textbf{FastAPI}, reducing project timelines by 50\%.}
    \end{cvitems}
  }
  %---------------------------------------------------------
  \cventry
  {Full Stack Developer (Part-time)} % Job title
  {ArcDesign} % Organization
  {Spain (Remote)} % Location
  {Jul. 2023 - March. 2025} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed an advanced geolocation algorithm with \textbf{hashmaps} and \textbf{geohashes}, resulting in a 70\% improvement in scalability and accuracy.}
      \item {Integrated the algorithm with \textbf{React Native}, enhancing mobile app performance, responsiveness, and UX.}
      \item {Deployed static websites using \textbf{React} on \textbf{AWS} and Hostinger, ensuring reliable and scalable architecture for clients.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Problem Solver / Full Stack Developer} % Job title
  {Design Systems Inno} % Organization
  {Colombia} % Location
  {Dec. 2022 - Jun. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed cloud-native API architectures using \textbf{RabbitMQ} and \textbf{MongoDB} for real-time, asynchronous data processing.}
      \item {Optimized \textbf{React} and \textbf{Angular} application builds, achieving 70\% reduction in bundle sizes and significantly faster load times across devices.}
      \item {Built \textbf{React (Redux + Saga)} admin panels with \textbf{TypeScript}, managing complex state and real-time data visualization.}
      \item {Improved \textbf{Docker} containerization strategies for both \textbf{React} and \textbf{Angular} applications, improving the \textbf{CI/CD} pipeline.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Cyber Security Analyst} % Job title
  {Geta Club Play} % Organization
  {Colombia (Remote)} % Location
  {Sep. 2021 - Jun. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Established a robust \textbf{DevSecOps} pipeline using \textbf{OWASP ZAP} and \textbf{SonarQube}, reducing project vulnerabilities by 50\% in 4 months.}
      \item {Collaborated with cross-functional teams to develop a security plan based on \textbf{ISO/27001} standards.}
      \item {Performed reverse engineering to safeguard APKs, identifying and mitigating potential data leaks that reduced critical vulnerabilities by 40\%.}
    \end{cvitems}
  }

\end{cventries}