%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
\documentclass[11pt,a4paper]{awesome-cv}
\usepackage[hidelinks]{hyperref}

\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}
\colorlet{awesome}{awesome-red}
\setbool{acvSectionColorHighlight}{true}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\definecolor{darktext}{HTML}{1A1A1A}
\colorlet{text}{darktext}
\renewcommand*{\lettertextstyle}{\fontsize{10pt}{1.45em}\bodyfontlight\upshape\color{darktext}}
\renewcommand*{\lettersectionstyle}[1]{{\fontsize{14pt}{1em}\bodyfont\bfseries\color{darktext}#1}}

% --- Header info ---
\name{Juan Manuel}{Young Hoyos}
\position{Frontend Engineer — React / TypeScript / Nuxt.js}
\address{Medellín, Colombia · Open to Remote / Hybrid (Japan)}
\mobile{+57 1234567890}
\email{juanmanuel12.13jmyh81@gmail.com}
\homepage{jmyounghoyos.com}
\github{Youngermaster}
\linkedin{juan-manuel-young-hoyos}

% --- Letter meta ---
\recipient
  {Hiring Team}
  {PayPay Card Corporation}
\letterdate{\today}
\lettertitle{Application for Frontend Engineer — PayPay Card}
\letteropening{Dear PayPay Card Hiring Team,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Resume — Juan Manuel Young Hoyos.pdf}

\begin{document}
\makecvheader[R]
\makelettertitle

\begin{cvletter}

I am writing to apply for the \textbf{Frontend Engineer} position at PayPay Card. I build production web and mobile interfaces with \textbf{TypeScript}, \textbf{React/Next.js}, and more recently \textbf{Nuxt.js} in a mixed Vue environment, and I’m very interested in contributing to a high-traffic, payments-related mini app like yours.

At \textbf{Publicis Global Delivery}, I have shipped customer-facing features using \textbf{Next.js + TypeScript} and also worked on an internal \textbf{Nuxt.js} web app, so I am comfortable with the Vue 3 / TS component model, API integration patterns, and working with design systems. I manage CI/CD with \textbf{GitHub Actions}, and I’ve used monitoring tools similar to \textbf{Sentry} and Dynatrace to keep UIs stable in production — which matches the stack you described (Nuxt 3, OpenAPI, GitHub, static deploys on AWS).

Across my roles (PGD, Grisú, ArcDesign) I’ve had to collaborate with distributed teams, clarify requirements with product/design, and keep frontend codebases maintainable and performance-oriented. That’s why I’m especially interested in your plan to \textbf{re-assess and update the frontend architecture}: I enjoy refactoring toward scalable patterns, strict typing, and API-first integration.

I work in English on a daily basis and I’m comfortable in multicultural teams. I am open to a hybrid/remote setup from LATAM and to aligning with Japan working practices.

Thank you for your time and consideration. I would be happy to help PayPay Card deliver a fast, reliable, and well-structured frontend for its users.

\end{cvletter}

\makeletterclosing
\end{document}
