\cvsection{Experience}
\newcommand{\quotes}[1]{``#1''}

\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Technical Lead}
  {Okorum Technologies}
  {Medellín, Colombia (Hybrid)}
  {Dec. 2025 -- Present}
  {
    \begin{cvitems}
      \item {Shipped a nationally-compliant health-interoperability platform \textbf{ahead of the government mandate deadline} by architecting a \textbf{Turborepo monorepo of NestJS (Node.js) microservices} that stream send / validate / convert / generate stages over \textbf{message queues} into \textbf{HL7 FHIR R4}.}
      \item {Kept the \textbf{data pipeline} fast and resilient under multi-provider load with a \textbf{Redis} cache and \textbf{fault-tolerant, resumable queues} that recover from an unreliable upstream API (\textbf{MongoDB} persistence).}
      \item {Led a cross-functional engineering team and gave it production visibility via \textbf{observability} (\textbf{Grafana}, \textbf{Loki}) and \textbf{CI/CD on AWS} (GitHub Actions).}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Frontend Developer}
  {Publicis Global Delivery (PGD) — assigned to Digitas}
  {Colombia (Remote)}
  {Jan. 2025 -- Present}
  {
    \begin{cvitems}
      \item {Improved load performance and delivered \textbf{responsive UX} across desktop / tablet / mobile by leading the redesign of Duluth Trading Company's e-commerce in \textbf{Next.js} + \textbf{TypeScript}, owning implementation, review and \textbf{CI/CD} rollout.}
      \item {Raised workflow reliability for distributed internal teams by shipping production features and stability fixes to an internal \textbf{AI-agent web app} (\textbf{Nuxt.js}) --- \textbf{AI-powered internal tooling}.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {React Native Developer}
  {Publicis Global Delivery (PGD) — assigned to Razorfish / Wegmans}
  {Colombia (Remote \textemdash{} New York)}
  {Dec. 2023 -- Dec. 2024}
  {
    \begin{cvitems}
      \item {Increased in-app engagement by \textbf{30\%} for Wegmans Food Markets by delivering \textbf{production React Native features} --- modular components in \textbf{TypeScript}, \textbf{Zustand} and \textbf{Algolia}.}
      \item {Cut critical bugs by \textbf{25\%} and reduced regression risk by integrating \textbf{Dynatrace} observability and \textbf{Jest} unit tests.}
      \item {Reduced release-cycle time by \textbf{50\%} by automating \textbf{CI/CD} for Android / iOS builds with GitHub Actions.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Full Stack Developer (Self-employed)}
  {Grisú}
  {Colombia (Remote)}
  {Jul.\ 2023 -- Present}
  {
    \begin{cvitems}
      \item {Delivered full-stack web apps for stakeholders (incl. public-sector programs in Curaçao) by building with \textbf{NestJS} + \textbf{React} and shipping to \textbf{Azure} with secured CI/CD pipelines.}
      \item {Compressed a 4-month plan into weeks by auditing and accelerating the \textbf{EcoDrive} project --- an \textbf{event-driven} system built with \textbf{React Native}, \textbf{Kafka} and \textbf{Python FastAPI}.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Earlier Experience --- Full-Stack, Backend \& Security}
  {ArcDesign · Design Systems Inno · Geta Club Play \& Aligo}
  {Colombia / Spain (Remote \& Hybrid)}
  {Sep.\ 2021 -- Jun.\ 2023}
  {
    \begin{cvitems}
      \item {Built internal \textbf{REST APIs} (\textbf{Go Fiber}, \textbf{Python FastAPI}, \textbf{MongoDB}) with \textbf{RabbitMQ}-based async task orchestration, and cut React / Angular bundle sizes from 3.46 MB to \textbf{~886 KB} (Design Systems Inno).}
      \item {Designed a \textbf{geohash + hashmap} geolocation algorithm and integrated it into \textbf{React Native} for near real-time UX; deployed React sites to \textbf{AWS} / Hostinger (ArcDesign).}
      \item {Reduced known vulnerabilities by \textbf{50\%} in 4 months via \textbf{DevSecOps} pipelines (OWASP ZAP, SonarQube) and Python automation (Geta Club Play \& Aligo).}
    \end{cvitems}
  }

\end{cventries}
