\cvsection{Experience}
\newcommand{\quotes}[1]{``#1''}

\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Frontend Developer}
  {Publicis Global Delivery (PGD) — assigned to Digitas}
  {Colombia (Remote)}
  {Jan. 2025 -- Present}
  {
    \begin{cvitems}
      \item {Led the redesign of Duluth Trading Company's e-commerce using \textbf{Next.js} + \textbf{TypeScript}, improving load performance and a \textbf{responsive UX}.}
      \item {Shipped production features and stability fixes to an internal \textbf{AI agent web app} (\textbf{Nuxt.js}), improving workflow reliability for distributed teams.}
      \item {Owned the full delivery loop: implementation, code review, performance tuning, and rollout with CI/CD.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {React Native Developer}
  {Publicis Global Delivery (PGD) — assigned to Razorfish / Wegmans}
  {Colombia (Remote \textemdash{} New York)}
  {Dec.\ 2023 -- Dec.\ 2024}
  {
    \begin{cvitems}
      \item {Delivered \textbf{production React Native features} at scale for Wegmans Food Markets, Inc.; modular components (\textbf{TypeScript}, \textbf{Zustand}, \textbf{Algolia}).}
      \item {Improved reliability using \textbf{Dynatrace} monitoring and \textbf{Jest} unit tests, reducing critical bugs by \textbf{25\%}.}
      \item {Automated \textbf{CI/CD pipelines} for Android/iOS with GitHub Actions, reducing release cycle time by \textbf{50\%}.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Full Stack Developer (Self-employed)}
  {Grisú}
  {Colombia (Remote)}
  {Jul.\ 2023 -- Present}
  {
    \begin{cvitems}
      \item {Deployed infrastructure for a public-sector project in Curaçao on \textbf{Azure}, using \textbf{VMs}, \textbf{Azure Database for PostgreSQL}, and \textbf{App Service}, with automated \textbf{CI/CD via GitHub Actions} and backup replication for reliability.}
      % \item {Developed full-stack applications with \textbf{NestJS + React}, leveraging \textbf{Azure cloud dependencies} and monitoring with \textbf{Grafana} and \textbf{Dynatrace}.}
      \item {Built and deployed \textbf{GameConnect}, an internal platform using \textbf{React}, \textbf{NestJS}, and \textbf{Kafka}, deployed on \textbf{AWS} (EC2, RDS, S3) for real-time event processing and analytics dashboards.}
      \item {Worked directly with stakeholders to translate requirements into reliable, scalable deployments, and performed code audits.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Full Stack Developer (Part-time)}
  {ArcDesign}
  {Spain (Remote)}
  {Jul.\ 2023 -- Mar.\ 2025}
  {
    \begin{cvitems}
      \item {Designed distributed backend architecture using \textbf{Go} microservices and message queues (Kafka, RabbitMQ) for real-time telemetry processing.}
      \item {Implemented a geolocation algorithm using \textbf{hashmaps + geohashes}, improving scalability and accuracy.}
      \item {Integrated that logic in \textbf{React Native} for fast, near real-time UX.}
      \item {Provisioned and deployed production environments on \textbf{AWS} (EC2, RDS, S3), ensuring availability and observability.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Problem Solver / Full Stack Developer}
  {Design Systems Inno}
  {Medellín, Colombia (Hybrid)}
  {Dec.\ 2022 -- Jun.\ 2023}
  {
    \begin{cvitems}
      \item {Designed internal APIs using \textbf{Go Fiber}, \textbf{Python FastAPI}, and \textbf{MongoDB} with \textbf{RabbitMQ} for asynchronous task handling.}
      \item {Implemented and deployed internal tools on \textbf{AWS} leveraging S3, Lambda, and ECS to improve developer productivity and CI/CD automation.}
      \item {Created React dashboards (Redux + Saga) and optimized React and Angular builds, reducing bundle sizes from 3.46 MB to ~886 KB.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Cyber Security Analyst / Red Team}
  {Geta Club Play \& Aligo}
  {Colombia}
  {Sep.\ 2021 -- Oct.\ 2022}
  {
    \begin{cvitems}
      \item {Collaborated with DevOps engineers to manage infrastructure provisioning with \textbf{Terraform on Azure}, defining \textbf{multi-environment deployments} (dev, QA, prod) to ensure rapid recovery and compliance with \textbf{ISO reliability standards}.}
      \item {Implemented \textbf{DevSecOps pipelines} using \textbf{OWASP ZAP} and \textbf{SonarQube}, reducing vulnerabilities by \textbf{50\%} in four months.}
      % \item {Automated static code analysis and secure builds in CI/CD pipelines, improving deployment reliability and traceability.}
      \item {Wrote Python scripts for system monitoring and log analysis to detect early anomalies in backend and mobile systems.}
    \end{cvitems}
  }

\end{cventries}
