%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
\newcommand{\quotes}[1]{``#1''}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Full Stack Developer} % Job title
  {Grisú} % Organization
  {Self-employed, Colombia} % Location
  {Jul. 2023 - Present (Aug. 2023)} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Engineered the company's landing page using \textbf{React}, boosting the site's traffic by 150\%.}
      \item {Designed and deployed a \textbf{React Native} App, Yak Bak 90's toy simulator.}
      \item {Serving as an auditor and developer to 'EcoDrive', using \textbf{React Native} and \textbf{Python Fast API}, reducing a 4-month timeline to weeks.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Full Stack Developer} % Job title
  {ArcDesign} % Organization
  {Part-time, Spain} % Location
  {Jul. 2023 - Present (Aug. 2023)} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Innovated an advanced algorithm using hashmaps, MQTT and geohashes, enhancing the application's performance by 70\%.}
      \item {Integrated the algorithm in a \textbf{React Native} environment, improving mobile app performance. (https://hiwayapp.io)}
      \item {Led the deployment of several static websites on \textbf{AWS} and Hostinger using \textbf{React}. (https://arcdesign.io)}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Problem Solver} % Job title
  {Design Systems Inno} % Organization
  {Contract, Colombia} % Location
  {Jan. 2023 - Jun. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Architected a system for internal APIs using \textbf{RabbitMQ}, improving asynchronous task efficiency by 40\%.}
      \item {Developed internal APIs to automate processes using \textbf{Go}, \textbf{Python Fast API}, and \textbf{MongoDB}, resulting in a 25\% time saving in task executions.}
      \item {Reduced \textbf{React} web applications' build sizes from 3.46 MB to 886 KB, optimizing loading times by 60\%.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Security Consultant} % Job title
  {Design Systems Inno} % Organization
  {Contract, Colombia} % Location
  {Dec. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Conducted an external penetration testing, identifying and
                  documenting potential security flaws, which led to a 70\% reduction in system vulnerabilities.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Red Teamer} % Job title
  {Aligo Defensores Informáticos} % Organization
  {In person, Colombia} % Location
  {Aug. 2022 - Oct. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Conducted pentests on several websites, improving their security postures by 50\%.}
      \item {Developed pentesting tools using \textbf{Go} and \textbf{Nim}, increasing the efficiency of the team's operations by 35\%.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Cyber Security Analyst} % Job title
  {GETA Club Play} % Organization
  {Remote, Colombia} % Location
  {Oct. 2021 - Jun. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Implemented \textbf{DAST} and \textbf{SAST} capabilities using \textbf{OWASP ZAP} and \textbf{SonarQube}, identifying and resolving over 410 vulnerabilities in 4 months.}
      \item {Developed a security plan based on \textbf{ISO/27001}, establishing a foundation for the company's long-term cybersecurity strategy.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Cyber Security Trainee} % Job title
  {GETA Club Play} % Organization
  {Remote, Colombia} % Location
  {Aug. 2021 - Sep. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Conducted Cyber security planning for 3 company products, identifying and rectifying OWASP vulnerabilities.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Software Quality Assurance Tester} % Job title
  {GETA Club Play} % Organization
  {Remote, Colombia} % Location
  {Feb. 2021 - Jul. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Detected 200+ bugs across 7 products in 6 months doing manual testing and automating it with \textbf{Python Selenium}.}
    \end{cvitems}
  }
  %---------------------------------------------------------
\end{cventries}
