%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
\documentclass[11pt, a4paper]{awesome-cv}
\usepackage[hidelinks]{hyperref}

\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% ---- Color Scheme ----
\colorlet{awesome}{awesome-emerald}
\setbool{acvSectionColorHighlight}{true}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

% ---- Text Contrast ----
\definecolor{darktext}{HTML}{1A1A1A}
\colorlet{text}{darktext}
\colorlet{graytext}{darktext}
\colorlet{lighttext}{darktext}
\renewcommand*{\lettertextstyle}{\fontsize{10pt}{1.45em}\bodyfontlight\upshape\color{darktext}}
\renewcommand*{\lettersectionstyle}[1]{{\fontsize{14pt}{1em}\bodyfont\bfseries\color{darktext}#1}}

% --- Header ---
\name{Ana Maria}{Hoyos Soto}
\position{Early Childhood Assistant {\enskip\cdotp\enskip} Childcare Support | Team Collaboration}
\address{Medellín, Colombia}
\mobile{+57 1234567890}
\email{amhsoto.09@gmail.com}
\linkedin{ana-maria-hoyos-soto-0b8a1b385}

% --- Letter meta ---
\recipient{Hiring Manager}{Precious Lambs Early Years Centre \\ 61 Pope Rd, Summerside, PE, Canada}
\letterdate{\today}
\lettertitle{Application for Early Childhood Educator (ECE) Assistant Position}
\letteropening{Dear Hiring Manager,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Resume — Ana Maria Hoyos Soto.pdf}

\begin{document}
\makecvheader[R]
\makelettertitle

\begin{cvletter}

I am writing to express my interest in the \textbf{Early Childhood Educator (ECE) Assistant} position at \textbf{Precious Lambs Early Years Centre}. I am an experienced administrative professional with over 8 years of experience supporting people, organizing activities, and maintaining structured, positive environments — skills that align perfectly with assisting educators and caring for children.

Throughout my career at \textbf{Inversiones Cadutex C.A.}, I demonstrated reliability, teamwork, and strong communication while helping manage day-to-day operations and ensuring the well-being of both staff and clients. Additionally, I have volunteered at community events supporting children’s activities, helping with crafts, reading sessions, and games that encouraged social and emotional growth. These experiences strengthened my ability to guide, assist, and connect with children in a nurturing way.

I am a patient, caring, and organized person who values creating safe and engaging environments for children to learn and grow. I am confident that my dedication, adaptability, and compassion will make me a positive addition to your team. I am also open to relocation and ready to start as soon as possible.

Thank you for considering my application. I would be happy to provide any additional information or references and look forward to the opportunity to contribute to the meaningful work you do at Precious Lambs Early Years Centre.

\end{cvletter}

\makeletterclosing
\end{document}
