\cvsection{Experience}

\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Frontend Developer}
  {Publicis Global Delivery (PGD) — assigned to Digitas}
  {Colombia (Remote)}
  {Jan. 2025 -- Present}
  {
    \begin{cvitems}
      \item {Led the redesign of Duluth Trading Company's e-commerce using \textbf{Next.js} + \textbf{TypeScript}, improving load performance and delivering \textbf{responsive UX} across desktop / tablet / mobile.}
      \item {Collaborated with UX \& design teams to translate requirements into \textbf{accessible, maintainable UI components}.}
      \item {Shipped production features and stability fixes to an internal \textbf{AI agent web app} (\textbf{Nuxt.js}), improving workflow reliability for distributed teams.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {React Native Developer}
  {Publicis Global Delivery (PGD) — assigned to Razorfish / Wegmans}
  {Colombia (Remote \textemdash{} New York)}
  {Dec. 2023 -- Dec. 2024}
  {
    \begin{cvitems}
      \item {Delivered and maintained \textbf{production React Native apps} for Wegmans Food Markets, Inc., integrating secure transactions and analytics features.}
      \item {Built modular components with \textbf{TypeScript}, \textbf{Zustand}, and \textbf{Algolia}, boosting engagement by \textbf{30\%}.}
      \item {Implemented monitoring with \textbf{Dynatrace} and wrote \textbf{unit tests (Jest)} to cut bugs by \textbf{25\%}.}
      \item {Automated \textbf{CI/CD pipelines} for Android/iOS builds using GitHub Actions, reducing release cycle time by \textbf{50\%}.}
      \item {Handled internal deployment testing flows and contributed to publishing processes for \textbf{App Store} and \textbf{Play Store}.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Full Stack Developer (Self-employed)}
  {Grisú}
  {Colombia (Remote)}
  {Jul.\ 2023 -- Present}
  {
    \begin{cvitems}
      \item {Developed and deployed \textbf{3+ React Native \& Flutter apps} to production, focusing on reliability, cloud integration, and CI/CD. (+ some incoming)}
      \item {Architected full-stack apps with \textbf{NestJS} + \textbf{React}, deployed to \textbf{Azure}, and secured with role-based authentication.}
      \item {Developed full-stack web apps with \textbf{NestJS} + \textbf{React}; shipped to \textbf{Azure} with \textbf{cloud service dependencies} and secured CI/CD pipelines.}
      \item {Audited and accelerated the \textbf{EcoDrive} project (React Native + Kafka + Python FastAPI), compressing a 4-month plan into weeks.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Full Stack Developer (Part-time)}
  {ArcDesign}
  {Spain (Remote)}
  {Jul.\ 2023 -- Mar.\ 2025}
  {
    \begin{cvitems}
      \item {Implemented a geolocation algorithm using \textbf{hashmaps + geohashes}, improving scalability and accuracy.}
      \item {Built and deployed \textbf{3 production React Native apps} with real-time features and high-availability APIs.}
      \item {Deployed React-based sites to AWS/Hostinger.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Problem Solver / Full Stack Developer}
  {Design Systems Inno}
  {Medellín, Colombia (Hybrid)}
  {Dec.\ 2022 -- Jun.\ 2023}
  {
    \begin{cvitems}
      \item {Led the development of a \textbf{React Native access control app} integrating \textbf{AWS Rekognition} for facial authentication.}
      \item {Designed internal APIs with \textbf{Go Fiber}, \textbf{FastAPI}, and \textbf{MongoDB} using \textbf{RabbitMQ} for async processing.}
      \item {Optimized React and Angular builds, cutting bundle sizes from 3.46 MB to \textbf{~886 KB} and improving load time significantly.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Cyber Security Analyst / Red Team}
  {Geta Club Play \& Aligo}
  {Colombia}
  {Sep.\ 2021 -- Oct.\ 2022}
  {
    \begin{cvitems}
      \item {Implemented DevSecOps pipelines using \textbf{OWASP ZAP} and \textbf{SonarQube}, reducing vulns by \textbf{50\%} in 4 months.}
      \item {Reverse engineered APKs to detect sensitive info exposure and worked with devs to mitigate.}
    \end{cvitems}
  }

\end{cventries}
