\cvsection{Experience}
\newcommand{\quotes}[1]{``#1''}

\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Frontend Developer}
  {Publicis Global Delivery (PGD) — assigned to Digitas}
  {Colombia (Remote)}
  {Jan. 2025 -- Present}
  {
    \begin{cvitems}
      \item {Collaborated with UX \& design teams to translate requirements into \textbf{accessible, maintainable UI components} using Next.js + TypeScript.}
      \item {Led the redesign of Duluth Trading Company's e-commerce using \textbf{Next.js} + \textbf{TypeScript}, improving load performance and delivering \textbf{responsive UX} across desktop / tablet / mobile.}
      \item {Shipped production features and stability fixes to an internal \textbf{AI agent web app} (\textbf{Nuxt.js}), improving workflow reliability for distributed teams.}
      \item {Owned the full delivery loop: implementation, code review, performance tuning, and rollout with CI/CD.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {React Native Developer}
  {Publicis Global Delivery (PGD) — assigned to Razorfish / Wegmans}
  {Colombia (Remote \textemdash{} New York)}
  {Dec. 2023 -- Dec. 2024}
  {
    \begin{cvitems}
      \item {Delivered \textbf{production React Native features} at scale for Wegmans Food Markets, Inc.; modular components (\textbf{TypeScript}, \textbf{Zustand}, \textbf{Algolia}) increased in-app engagement by \textbf{30\%}.}
      \item {Improved app reliability by integrating \textbf{Dynatrace} observability and \textbf{Jest} unit tests, cutting critical bugs by \textbf{25\%} and reducing regression risk.}
      \item {Automated \textbf{CI/CD} with GitHub Actions for Android/iOS builds and releases, reducing release cycle time by \textbf{50\%} and supporting iterative delivery.}
      \item {Implemented responsive, accessible UI for touch and keyboard input, focusing on performance and predictable state.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Full Stack Developer (Self-employed)}
  {Grisú}
  {Colombia (Remote)}
  {Jul.\ 2023 -- Present}
  {
    \begin{cvitems}
      \item {Developed full-stack web apps with \textbf{NestJS} + \textbf{React}; shipped to \textbf{Azure} with \textbf{cloud service dependencies} and secured CI/CD pipelines.}
      \item {Worked directly with stakeholders (including public-sector programs in Curaçao) to gather requirements, build quickly, and iterate.}
      \item {Audited and accelerated the \textbf{EcoDrive} project (React Native + Kafka + Python FastAPI), compressing a 4-month plan into weeks.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Full Stack Developer (Part-time)}
  {ArcDesign}
  {Spain (Remote)}
  {Jul.\ 2023 -- Mar.\ 2025}
  {
    \begin{cvitems}
      \item {Implemented a geolocation algorithm using \textbf{hashmaps + geohashes}, improving scalability and accuracy.}
      \item {Integrated that logic in \textbf{React Native} for fast, near real-time UX.}
      \item {Deployed React-based sites to AWS/Hostinger.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Problem Solver / Full Stack Developer}
  {Design Systems Inno}
  {Medellín, Colombia (Hybrid)}
  {Dec.\ 2022 -- Jun.\ 2023}
  {
    \begin{cvitems}
      \item {Designed internal APIs using \textbf{Go Fiber}, \textbf{Python FastAPI} and \textbf{MongoDB} with \textbf{RabbitMQ} for async tasks.}
      \item {Created React dashboards (Redux + Saga) and \textbf{optimized React and Angular builds}, reducing bundle sizes from 3.46 MB to \textbf{~886 KB}.}
      \item {Improved Dockerfiles for \textbf{React and Angular} apps to speed up CI/CD. Paired with teammates to fix critical bugs before delivery.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Cyber Security Analyst / Red Team}
  {Geta Club Play \& Aligo}
  {Colombia}
  {Sep.\ 2021 -- Oct.\ 2022}
  {
    \begin{cvitems}
      \item {Implemented DevSecOps pipelines using \textbf{OWASP ZAP} and \textbf{SonarQube}, reducing vulns by \textbf{50\%} in 4 months.}
      \item {Reverse engineered APKs to detect sensitive info exposure and worked with devs to mitigate.}
      \item {Wrote automation scripts in Python and contributed to secure coding practices.}
    \end{cvitems}
  }

\end{cventries}
