%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activities}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Participant} % Affiliation/role
    {CivicaPay Hackathon 2022} % Organization/group
    {Medellín} % Location
    {Mar. 2022 - Mar. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {\textbf{First place} achieved among more than 50 teams and 16 universities in 
        Medellín in the Hackathon CivicaPay of 2022.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Youngermaster - Script kiddie} % Affiliation/role
    {HackTheBox} % Organization/group
    {Worldwide} % Location
    {Dec. 2021 - Present (Mar. 2022)} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {\href{https://app.hackthebox.com/rankings/country/CO}{22th in Colombia Ranking.}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Chrome Web Store} % Affiliation/role
    {Developer} % Organization/group
    {Worldwide} % Location
    {Jan. 2022 - Jan. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {\href{https://chrome.google.com/webstore/detail/platzi-community-wrapper/dakgbbfpefoofghfbkopnbnpadeblbep}
        {I pusblished an extension to remove the Platzi's academy comments.}}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Google Play Store} % Affiliation/role
    {Mobile developer} % Organization/group
    {Worldwide} % Location
    {Nov. 2019 - Apr. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {\href{https://play.google.com/store/apps/details?id=com.grisu.accelerometer}{
        \textbf{Accelerometer} - An app with more than 100 downloads using Flutter to obtain the data from your accelerometer
        in a time 'x', with time intervals 'y' in milliseconds and send the information wherever you
        want (Email, WhatsApp, etc.), and store that information in a txt file on your phone to be
        used in another scenarios.}}
        \item {\href{https://play.google.com/store/apps/details?id=com.grisu.anthropometric_evaluator}{
          \textbf{Anthropometric Evaluator} - An application using Flutter that provides information
          and evaluates some of the parts of your body with certain measurements to provide a more
          complete analysis than the common BMI, for people who go to the gym.}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://github.com/Youngermaster}{GitHub Contributor}} % Affiliation/role
    {\href{https://github.com/Youngermaster}{GitHub}} % Organization/group
    {Worldwide} % Location
    {Feb. 2018 - Present (March. 2022)} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {\href{https://github.com/Youngermaster}{+1800 total contributions.}}
        \item {\href{https://github.com/Youngermaster}{+140 public repositories.}}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
