%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
\newcommand{\quotes}[1]{``#1''}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Frontend Developer} % Job title
  {Publicis Global Delivery (PGD) assigned to Digitas} % Organization
  {Colombia (Remote)} % Location
  {Jan. 2025 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {I implemented the redesign of Publicis Collective's new website using \textbf{Nuxt.js} and \textbf{Contentful}.}
      \item {I collaborated with bug fixes and improvements on the \textbf{Nuxt.js} AI agent web app to support the marketing team in their daily tasks.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {React Native Developer} % Job title
  {Publicis Global Delivery (PGD) assigned to Razorfish} % Organization
  {Colombia (Remote - New York, USA)} % Location
  {Dec. 2023 - Dec. 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Collaborated with Razorfish in New York on the \textbf{Wegmans} mobile app, delivering scalable \textbf{React Native} components and integrating \textbf{Zustand} and \textbf{Algolia}, resulting in a 30\% increase in user engagement and conversion rates.}
      \item {Implemented performance monitoring with \textbf{Dynatrace}, achieving a 40\% enhancement in system reliability and response times.}
      \item {Added unit testing using \textbf{Jest}, boosting code coverage and reducing bugs by 25\%, significantly improving app stability.}
      \item {Streamlined the CI/CD pipeline with \textbf{GitHub Actions}, reducing deployment time by 50\% and accelerating delivery for the Wegmans app.}
    \end{cvitems}
  }

  %---------------------------------------------------------
 \cventry
  {Full Stack Developer (Self-employed)} % Job title
  {Grisú} % Organization
  {Colombia (Remote)} % Location
  {Jul. 2023 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Partnered with the \textit{Curaçao} government for the \textit{Ministerie van Sociale Ontwikkeling, Arbeid en Welzijn (SOAW)} to enhance their web app, improving performance with \textbf{Nest.js (TypeScript)} and \textbf{React}, leading to smoother access for citizens requesting social assistance.}
      \item {Provided strategic architectural guidance to \textit{GameConnect} and \textit{Industrias Falcon}, delivering performance-optimized solutions for UI/UX.}
      \item {Accelerated the project timeline for \textbf{EcoDrive} by 50\% through an efficient combination of \textbf{React Native}, \textbf{Kafka}, and \textbf{FastAPI}.}
    \end{cvitems}
  }
  %---------------------------------------------------------
  \cventry
  {Full Stack Developer (Part-time)} % Job title
  {ArcDesign} % Organization
  {Spain (Remote)} % Location
  {Jul. 2023 - March. 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed an advanced geolocation algorithm with \textbf{hashmaps} and \textbf{geohashes}, resulting in a 70\% improvement in scalability and accuracy.}
      \item {Integrated the algorithm with \textbf{React Native}, enhancing mobile app performance, responsiveness, and UX.}
      \item {Spearheaded the deployment of static websites on \textbf{AWS} and Hostinger, ensuring reliable and scalable architecture for clients.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Problem Solver / Full Stack Developer} % Job title
  {Design Systems Inno} % Organization
  {Colombia} % Location
  {Dec. 2022 - Jun. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Architected a highly responsive API system using \textbf{RabbitMQ} and \textbf{MongoDB} for asynchronous task processing, significantly improving load handling and user feedback efficiency.}
      \item {Enhanced project builds for \textbf{React} applications, reducing load sizes by 70\%, resulting in improved performance and faster load times for users.}
      \item {Developed and optimized complex \textbf{React (Redux + Saga)} admin panels, improving data management and visualization capabilities.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Cyber Security Analyst} % Job title
  {Geta Club Play} % Organization
  {Colombia (Remote)} % Location
  {Sep. 2021 - Jun. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Established a robust \textbf{DevSecOps} pipeline using \textbf{OWASP ZAP} and \textbf{SonarQube}, reducing project vulnerabilities by 50\% in four months and enhancing application security.}
      \item {Collaborated with cross-functional teams to develop a security plan based on \textbf{ISO/27001} standards, ensuring data integrity and resilience against threats.}
      \item {Performed reverse engineering to safeguard APKs, identifying and mitigating potential data leaks that reduced critical vulnerabilities by 40\%.}
    \end{cvitems}
  }

\end{cventries}